Manuscript draft

### 2019-07-12 manuscript/manuscript draft.Rmd
updated manuscript draft

*Allocation to carbon fluxes along latitudinal gradients* Variation in allocation to component carbon fluxes along latitudinal gradients was explored for three sets of paired carbon fluxes: GPP:NPP; ANPP:BNPP; and ANPP~foliage~:ANPP~woodystem~. Three approaches were taken. Firstly, for each set of paired fluxes, measurements taken at the same site and plot, and in the same year, were paired together. The ratio of each pair of measurements was calculated. For each set of paired fluxes, the ratios were regressed against latitude and climate variables, using the linear model specified above. Additionally, sites were classified as "boreal", "temperate", or "tropical", using the FAO ecozone classifications from the ForC database. Non-parametric Wilcoxon t-tests were carried out to compare the ratio means between each pair of ecozone classifications.  
In addition, each carbon flux was regressed against latitude, and the models used to generate a series of point estimates along lines of best fit for each flux. For each pair of fluxes, the ratio of each point estimate was calculated and plotted, to gain an approximation of the variation of the ratio of the paired fluxes with latitude.

@@

*Do carbon fluxes vary in their responses to climate, particularly with regards to allocation between fluxes?*

```{r echo=FALSE, out.width='100%', fig.cap = "Ratio of ANPP foliage to ANPP woody stem plotted against major ecozones. All pairwise comparisons are significant. Significance levels of pairwise comparisons are indicated where * $p \\leq 0.05 $; ** $p \\leq 0.01 $; *** $p \\leq 0.001 $; **** $p \\leq 0.0001 $.", fig.pos='H'}
  knitr::include_graphics("boxplot_foliage_woodystem.png")
```

>>>>

*Allocation to carbon fluxes along latitudinal gradients.* Variation in allocation to component carbon fluxes along latitudinal gradients was explored for a range of pairings: firstly, GPP:NPP, ANPP:BNPP, and ANPP~foliage~:ANPP~woodystem~; and secondly, the ratio of NPP to each of ANPP, BNPP, ANPP~foliage~, and ANPP~woodystem~. For each set of paired fluxes, measurements taken at the same site and plot, and in the same year, were paired together, and the ratio of each pair of measurements calculated. The ratios were regressed against latitude and climate variables, using the linear model specified above. Cook's distance analyses were carried out for each of the models, and indicated that data from a few high-elevation sites were having a disproportionate influence on the regressions. To account for this, models were re-run using only data from sites $\leq$ 1000m.

@@

*Do carbon fluxes vary in their responses to climate, particularly with regards to allocation between fluxes?* Of all the flux pairings tested, the only ones to show a significant relationship with latitude were ANPP:NPP (p<0.01, r^2^ = 0.44) and ANPP:BNPP (p<0.001, r^2^ = 0.33). In both cases, allocation to ANPP increased with latitude, with the lowest allocation to ANPP in the tropical regions.
